---
title: "Occupational Data"
author: "Mary Hennigan" 
date: "1/26/2021"
output: pdf_document
---

# Compilation of Occupational COVID-19 Reports for Calculations

- **This notebook retrieves data from a Google sheet and compiles a time series of ADH occupational infection reports**

--**This 1/26 version created a time series from May 17 - Aug 20**

-**It will create a masterfile: occupation_master.csv**

# Part 1: Import Data, Clean It

```{r include=FALSE}
#install.packages("slider")
#install.packages("zoo")
#install.packages("gtools")
# vignette("basic-usage", package="googlesheets")
#install.packages("googledrive")
#install.packages("googlesheets4")
library(tidyverse)
library(janitor)
library(lubridate)
library(googlesheets4)
library(googledrive)
library(tidyr)
library(jsonlite)
library(gtools)
library(zoo)
library(reshape2)
library(slider)
```

#Import data from Hard Drive 
```{r}
 occupation5_25 <- rio::import("/Users/maryhennigan/Downloads/OSHA Project 2021/OccupationMaster.xlsx", which = "525 Occupational")
```

#Wells 
```{r}
 # occupation5_25 <- rio::import("/Users/rswells/Dropbox/Classes/Data Spring 2021/Facilities-Occupational Cases-Deaths.xlsx", which = "525 Occupational")


```


#This section for building the table from individual sheets
```{r include=FALSE}
 occupation5_25 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "525 Occupational")
 occupation5_29 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "529 Occupational")
 occupation6_2 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "62 Occupational")
 occupation5_25$date <- "2020-5-25"
 occupation5_29$date <- "2020-5-29"
 occupation6_2$date <- "2020-6-2"
 occupation6_5 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "65 Occupational")
 occupation6_9 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "69 Occupational")
 occupation6_12 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "612 Occupational")
 occupation6_14 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "614 Occupational")
 occupation6_18 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "618 Occupational")
 occupation6_5$date <- "2020-6-05"
 occupation6_9$date <- "2020-6-09"
 occupation6_12$date <- "2020-6-12"
 occupation6_14$date <- "2020-6-14"
 occupation6_18$date <- "2020-6-18"
 occupation6_25 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "625 Occupational")
 occupation6_28 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "628 Occupational")
 occupation7_3 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "73 Occupational")
 occupation7_6 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "76 Occupational")
 occupation6_25$date <- "2020-6-25"
 occupation6_28$date <- "2020-6-28"
 occupation7_3$date <- "2020-7-03"
 occupation7_6$date <- "2020-7-06"
 occupation7_14 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "714 Occupational")
 occupation7_21 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "721 Occupational")
 occupation7_24 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "724 Occupational")
 occupation8_3 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "83 Occupational")
 occupation8_7 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "87 Occupational")
 occupation7_14$date <- "2020-7-14"
 occupation7_21$date <- "2020-7-21"
 occupation7_24$date <- "2020-7-24"
 occupation8_3$date <- "2020-8-03"
 occupation8_7$date <- "2020-8-07"
 occupation8_10 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "810 Occupational")
 occupation8_20 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "820 Occupational")
 occupation8_10$date <- "2020-8-10"
 occupation8_20$date <- "2020-8-20"
```


```{r}
glimpse(occupation5_25)
```

```{r warning=FALSE}
occupation_master <- smartbind(occupation5_25, occupation5_29, occupation6_2, occupation6_5, occupation6_12, occupation6_14, occupation6_18, occupation6_25, occupation6_28, occupation6_9, occupation7_14, occupation7_21, occupation7_24, occupation7_3, occupation7_6, occupation8_10, occupation8_20, occupation8_3, occupation8_7)

occupation_master
```


